---
title: "Packaging functions"
author: "Lukasz A. Bartnik"
date: "August 29, 2015"
output: html_document
---

# Purpose of this document

This document describes the interface of the `package()` and
`package_()` functions. The former is designed for interactive use in
a R session, the latter is designed for programming R scripts and
packages.


# Packaging functions

One of the main goals of the `defer` package is to enable R users to
easily run complex scripts/sets of functions in a remote R session.
An important condition is to avoid complex object handling on the
side of the user and implement an automatic dependency detection
mechanism.

The dependencies might be of two kinds:
* dependencies on functions present in the global environment of the 
  current R session
* dependencies on library functions present in R packages installed
  in the local environment

The goal of the aforementioned dependency detection mechanism is to
discover all dependencies of both kinds and store them in a R object
that can be serialized, sent to a remote session, deserialized and
finally run. Running the package in a remote session should produce
the same exact results as running it locally.


# Sample packaging invocations

In order to help understand the concept of packaging, we provide as
number of examples of various ways to build an evaluation package.
We present both the interactive interface, that is, the `package()`
function, as well as the programmer interface, the `package_()`
function.


## The interactive interface

### Functions

```{r eval=FALSE}
fun <- function(x)x*x
package(fun)
```


```{r eval=FALSE}
package(function(x)x*x)
```


```{r eval=FALSE}
package({ x*x })
```


### Functions and dependencies

```{r eval=FALSE}
package({ x*x*fun(x) }, fun = function(z)log(z, 10))
```

If the dependency discovery mechanism cannot "see" the `log10()` function,
user can explicitely add `log10()` to the dependency list.

```{r eval=FALSE}
package({ x*x*log10(x) }, log10)
```


